\documentclass{article}
% article book report 

% first use latex , will gen *.(aux|dvi|log)
% then xdvi *.dvi ,gen pdf

% % 是注释的开始 行注释
\begin{document}

We hava seen that to typeset something in \LaTeX ,we type in text to be typeset together with some \LaTeX\   commands.
Words must be sparated by spaces (does not mater how many) and line maybe broken arbitrarily.

The end of a paragraph is specified by a \emph{blank line} in the input.In other words,whenever you want to start a new paragraph, juset leave a blank line and proceed.

\section{blank space}
% 当最后一个字符不是大写字符时,句号应该加上@变为@.
% 说明书上说最后一个字符不是大写需要加上@ 但是在我的工作环境下很好
Carrots are good for your eyes, since they contain Vitamin A. Have you ever seen a rabbit wearing glasses?

Carrots are good for your eyes, since they contain Vitamin A\@. Have you ever seen a rabbit wearing glasses?

The numbers 1, 2, 3, etc.\ are called natural numbers. According to Kronecker, they were made by God;all else being the works of Man.

The numbers 1, 2, 3, etc. are called natural numbers. According to Kronecker, they were made by God;all else being the works of Man.

%空格需要转义

% 一个段落过后应该是一个空行

\section{Quotes} %引号
% 使用 \lq \rq 表示左引号和右引号
% 在 命令后的空格确实需要转义空格,不然会识别为命令和文本之间的分隔符
\lq Wang Yang\rq\ is my name.\\
double lq is \lq\lq,and the right quotes is the same.
\section{dashes}
% 虚线
X-rays are discussed in pages 221--225 of Volume 3---the volume on electromagnetic waves.

\section{Accents}

% 音标  \''o 出问题了，打不出来 ''‘’
\`o \=o \u o \b o \'o \.o \v o \t oo \^o \''o \H o \~o \c c \d o


\'{E}l est\'{a} aqu\'{\i}

\oe\ \aa\ \o\ \ss\ !`\ \OE\ \AA\ \O\ ?` \ae\ \l\ \AE\ \L


\end{document}